The paper on \Large \bf Blockchain Frontrunning

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning] related work

\subsection{Front Running on the Blockchains}
\label{sec:Front Running on the Blockchains}

@@

~\cite{malinova2017market}
~\cite{aune2017footprints}
~\cite{breidenbach2018enter}

>>>>

\subsection{How are Blockchain Applications Vulnarable to Frontrunning?}
\label{sec:Front Running on the Blockchains}

@@

There are a few papers discussing frontrunning in the context of blockchain and decentral ledgers.

Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers ~\cite{malinova2017market}.  They argue that blockchain brings a new options of transparency which effects traders identity behaviour, specially in the presence of intermediately front runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make frontrunning costly and inefficient.

~\cite{aune2017footprints}
~\cite{breidenbach2018enter}

% Double spend papers: ~\cite{bamert2013have} ~\cite{karame2012double}
